---
title: "Untitled"
author: "Huanzhe Wang"
date: "October 14, 2015"
output: html_document
---
  
Required packages: Rcurl. 
```{r}
library(RCurl)
```


```{r}
fileURL <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv"
download.file(fileURL,destfile='gdp.csv',method='libcurl')
gdp<-read.csv('gdp.csv',skip=4,na.strings = c("..","Not available.","..Not available"),stringsAsFactors = F)
gdp<-dplyr::select(gdp,X,X.1,X.3,X.4)
names(gdp)<-c('CountryCode','Ranking','Economy','GDP')
gdp$Ranking<-as.numeric(gdp$Ranking)
a<-sum(is.na(gdp$Ranking))
gdp<-gdp[1:(nrow(gdp)-a),]
gdp$GDP<-as.numeric(gsub(",","", gdp$GDP))

fileurl<-'https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv'
download.file(fileurl,destfile='edu.csv',method='libcurl')
edu<-read.csv(file="edu.csv",header = T,stringsAsFactors = F)

```

# Match the data based on the country shortcode. How many of the IDs match? 
```{r}
match(gdp$CountryCode,edu$CountryCode)
```
#only left one NA and 189 obervations are available to have matched IDs.

# Sort the data frame,using descending order by GDP rank (so United States is last). What is the 13th country in the resulting data frame?
```{r}
gdp<-gdp[order(gdp$GDP,decreasing = F),]
gdp[13,]
```
#The 13th country is KNA(St. Kitts and Nevis).

# What are the average GDP rankings for the "High income: OECD" and "High income: nonOECD" groups? 
```{r}
gdp<-merge(gdp,edu,by='CountryCode')
gdp1<-gdp[which(gdp$Income.Group=='High income: OECD'),]
mean(gdp1$Ranking)
gdp2<-gdp[which(gdp$Income.Group=='High income: nonOECD'),]
mean(gdp2$Ranking)
```
#Average GDP rankings are 32.96667 and 91.91304.


# Cut the GDP ranking into 5 separate quantile groups. Make a table versus Income.Group. How many countries are Lower middle income but among the 38 nations with highest GDP?
```{r}
gdp$Rank.Group<-cut(gdp$Ranking,c(-Inf,38,76,114,152,Inf))
levels(gdp$Rank.Group)<-c('Lowest','Low','Middle','High','Highest')
table(gdp$Rank.Group,gdp$Income.Group)
```
#There show us 16 countries are belong to Lower middle income, but among the 38 nations with highest GDP.